Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-11-08 Manuscript_draft/Manuscript_draft.Rmd
p1

---
title: Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits 
author:
- affilnum: '1,2'
  name: Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
- affilnum: 3
  email: barragansljose@gmail.com
  name: Jose
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
- affil: Big Name University, Department of R, City, BN, 01020, USA
  affilnum: 2
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 3
output:
  word_document: null
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

@@

In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003. This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014. Once, the floral visitor has arrived to the flower, pollen deposition can take place and with an increasing number of visits the higher the chances of ovule fertilization (Refs).

I like what I have so far BUT we can make the story more complete

Moreover, once the pollinator has landed on the stigma some other issues for the plant species may arise, the arrival of foreign pollen and conspecific pollen loss @morales2008.

>>>>

---
title: Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits 
author:
- affilnum: '1,2,3'
  name: Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
  email: barragansljose@gmail.com
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
- affil: Big Name University, Department of R, City, BN, 01020, USA
  affilnum: 2
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 3
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  word_document: null
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

@@

In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003. This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014. Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and therefore ovule fertilization. An increasing number of visits generally correlates with higher chances of fertilization (Refs). However this is not always the case, among these flower visitors we find also nectar robbers and pollen thiefs (Refs) or pollen quality (example with ref?). Moreover, other less studies issues in the pollination process such as conspecific pollen loss or the arrival of foreign pollen can have detrimental effects for the species fitness @morales2008.

### 2018-11-08 Manuscript_draft/Manuscript_draft.tex
p1

\title{Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits}
\author{
Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
Jose
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader \textsuperscript{1,2} 
Jose \textsuperscript{*} \textsuperscript{3} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

In natural systems plant species normally coexist and share their floral
visitors with other species (Bascompte et al., 2003). This pollinator
sharing from the plant perpective can be negative due to competition
(refs) or positive due to facilitation Carvalheiro et al. (2014).
Moreover, once the pollinator has landed on the stigma some other issues
for the species fitness may arise, the arrival of foreign pollen and
conspecific pollen loss (Morales \& Traveset 2008)

@@

@@

>>>>

\title{Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits}
\author{
Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Working title, The impact of heterospecific pollen on plant reproductive
success is mediated by phylogenetic distance and floral reproductive
traits
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader \textsuperscript{*} \textsuperscript{1,2,3} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

In natural systems plant species normally coexist and share their floral
visitors with other species Bascompte et al. (2003). This pollinator
sharing from the plant perspective at the pre-pollination stage can be
negative due to competition Pauw (2013) or positive due to facilitation
Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
flower, pollen deposition on the stigma can take place and therefore
ovule fertilization. An increasing number of visits generally correlates
with higher chances of fertilization (Refs). However this is not always
the case, among these flower visitors we find also nectar robbers and
pollen thiefs (Refs) or pollen quality (example with ref?). Moreover,
other less studies issues in the pollination process such as conspecific
pollen loss or the arrival of foreign pollen can have detrimental
effects for the species fitness Morales and Traveset (2008).

@@

\hypertarget{ref-bascompte2003}{}
Bascompte, J., P. Jordano, C. J. Melián, and J. M. Olesen. 2003. The
nested assembly of plant--animal mutualistic networks. Proceedings of
the National Academy of Sciences 100:9383--9387.

@@

\hypertarget{ref-morales2008}{}
Morales, C. L., and A. Traveset. 2008. Interspecific pollen transfer:
Magnitude, prevalence and consequences for plant fitness. Critical
Reviews in Plant Sciences 27:221--238.

\hypertarget{ref-pauw2013}{}
Pauw, A. 2013. Can pollination niches facilitate plant coexistence?
Trends in ecology \& evolution 28:30--37.
